Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-18 R/model_fcs_markdown.Rmd
Update

@@

```{r}
draws2
mcmc_intervals(
  posterior1,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
mcmc_intervals(
  posterior2,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

>>>>

FCS sensu Helm et al. (2015) https://doi.org/10.1111/ddi.12285

@@

```{r}
draws1
mcmc_intervals(
  posterior1,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
mcmc_intervals(
  posterior2,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```
